On Secure Delegation of SampBQP with a Classical Client

### 2019-11-24 hamiltonian.tex
Fill in simple TODOs

First, for ease of notation, write

\begin{definition}
	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}}$. TODO maybe force at most $k$ non-identity components here?
\end{definition}

Then we define a certain form of quantum circuit that is still universal.

@@

\begin{definition}
	Let $C(x)$ be an XZ-circuit. Then let $H_{C(x)}$ be with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
		\item It has an eigenvector $\ket{\psi_{C(x)}}=TODO$ with eigenvalue $0$.
		\item Let $\ket\phi$ be such that $\braket{\phi|\psi_{C(x)}}=0$, then $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
	\end{itemize}
\end{definition}

@@

\begin{theorem}
	Given XZ-circuit $C$ and $x$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability... TODO that only uses $X$ and $Z$ measurements?
\end{theorem}

Lastly, before we present their proofs, we make an observation.

@@

TODO Combine and rewrite the following subsections

>>>>

First, fix $L\in\bbN$ and define the following that implicitly depends on $L$.

\begin{definition}
	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \norm{\set{i: U_i\ne I}}\leq L}$
\end{definition}

$L$ can be thought of as how ``local" the Hamiltonian is. Taking $L=5$ would easily suffice for this paper.

We define a certain form of quantum circuit that is still universal.

@@

\begin{definition}
	Let $C(x)$ be an XZ-circuit. Then let $H_{C(x)}$ be with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
		\item It has an eigenvector $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$.
		\item Let $\ket\phi$ be such that $\braket{\phi|\psi_{C(x)}}=0$, then $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
	\end{itemize}
\end{definition}

@@

\begin{theorem}
	Given XZ-circuit $C$ and $x$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$. Furthermore, this algorithm doesn't apply any quantum gates, and uses only $X$ and $Z$ measurements.
\end{theorem}

Lastly, before we present proofs for the above theorems, we make an observation.

@@
